---
title: "Bayes Tapas part antisaccades"
author: "Martyna"
date: "3/28/2019"
output: pdf_document
---
The following file contains models for the condition: ANTISACCADES.

I limited the diagnostic part to thoroughly analyzing models without test_retest and without prior.
```{r}
bayes = read.csv("~/dev/Prosaccades-Antisaccades/Data/bayes_annotated.csv")

# condition: 1 (anti), 2 (pro)
antisaccades = bayes[bayes$conditions == 1,]
prosaccades = bayes[bayes$conditions == 2,]

write.csv(antisaccades, "~/dev/Prosaccades-Antisaccades/Data/bayes_anti.csv", 
          row.names = FALSE)
write.csv(prosaccades, "~/dev/Prosaccades-Antisaccades/Data/bayes_pro.csv", 
          row.names = FALSE)

#bayes$late_pro_rt[bayes$conditions == 1] = NaN
#bayes$inhib_fail_rt[bayes$conditions == 1] = NaN
#bayes$anti_rt[bayes$conditions == 2] = NaN

write.csv(bayes, "~/dev/Prosaccades-Antisaccades/Data/bayes_annotated_nan.csv", 
          row.names = FALSE)

bayes_nan = read.csv("~/dev/Prosaccades-Antisaccades/Data/bayes_annotated_nan.csv")
antisaccades$age <- factor(antisaccades$age)
antisaccades$test_retest <- factor(antisaccades$test_retest)
```

Load required packages:
```{r}
library(brms)
theme_set(theme_default())
```


"Late prosaccade probability"

models:
```{r}
#models with priors
prior1 <- brms:::set_prior("cauchy(0,2.5)", class="b")
prior2 <- brms:::set_prior("cauchy(0,2)", class="b")
prior3 <- brms:::set_prior("cauchy(0,1)", class="b")

#model without prior and without test_retest
late_pro_prob_ac_withoutprior_withouttrt<- brm(late_pro_prob  ~ 1 + age, data = antisaccades, family = Beta(),save_all_pars = TRUE)

#model with test_retest and with prior 
late_pro_prob_ac_withtestrt_withprior<- brm(late_pro_prob  ~ 1 + age +test_retest, data = antisaccades, family = Beta(),save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with prior and without test_retest
late_pro_prob_ac_withprior_withouttrt<- brm(late_pro_prob  ~ 1 + age, data = antisaccades, family = Beta(),save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with test_retest and without prior 
late_pro_prob_ac_withtestrt_withoutprior<- brm(late_pro_prob  ~ 1 + age +test_retest, data = antisaccades, family = Beta(),save_all_pars = TRUE)

```

In further diagnostic I'll use model without test-retest and without prior
```{r}
#The results (i.e., posterior samples) can be investigated using
summary(late_pro_prob_ac_withoutprior_withouttrt)
#On the top of the output, some general information on the model is given, 
#such as family, formula, number of iterations and chains. Next, group-level effects are displayed seperately
#for each grouping factor in terms of standard deviations. On the bottom of the output, population-level effects
#(i.e. regression coefficients) are displayed. 

#To visually investigate the chains and the posterior distributions, we use: 
plot(late_pro_prob_ac_withoutprior_withouttrt, ask = FALSE)

#If we just want to see results of the regression coefficients of age and test_retest, we go for
plot(late_pro_prob_ac_withoutprior_withouttrt, pars = c("age", "test_retest")) 

#A more detailed investigation of the model:
#launch_shinystan(late_pro_prob_ac_c_withoutprior_withouttrt)

# Function fitter predict mean values of the response distribution (i.e., the 'regression line') for a fitted model. Can be performed for the data used to fit the model (posterior predictive checks) or for new data.
fitted_values_late_pro_prob_withoutprior_withouttrt <- fitted(late_pro_prob_ac_withoutprior_withouttrt)

head(fitted_values_late_pro_prob_withoutprior_withouttrt)

#We can perform posterior predictive checks
pp_late_pro_prob_ac_withoutprior_withouttrt = brms::pp_check(late_pro_prob_ac_withoutprior_withouttrt,nsamples = 100)

#To better understand the relationship of the predictors with the response, we can use the marginal_effects method:
plot(marginal_effects(late_pro_prob_ac_withoutprior_withouttrt, effects = "age"))
marginaleffects_late_pro_prob_ac_withoutprior_withouttrt <- brms::marginal_effects(late_pro_prob_ac_withoutprior_withouttrt, points = TRUE)
```

Custom plot of model predictions:
(we want to extract the data and make our own plot)
```{r}
#first we need to create new data set. We're interested in different levels of age
newdata = data.frame(age = levels(antisaccades$age))
fit = fitted(
 late_pro_prob_ac_withoutprior_withouttrt,
   newdata = newdata,
   re_formula = NA,
 summary = TRUE)
#we get fitted values for our model. We want just population - level predictions so we are interested in all participants
#in all ages =>we don't take random effect into account.
df_plot = cbind(newdata, fit)
#here we have both levels -old&young, the mean of the posterior distribution, the credible interval
df_plot
#we produce very similar plot that marginal effect function gives us, but here we can customize things - we can plot also the actual observed data: 
#(this graph show both the  observations and  the fitted values)
ggplot(df_plot, aes(x = age, y = Estimate)) +
  geom_violin(data=antisaccades, aes(x=age, y=late_pro_prob), alpha=0.5, color="gray70", fill='gray95') +
  geom_jitter(data=antisaccades, aes(x=age, y=late_pro_prob), alpha=0.3, position = position_jitter(width = 0.07)) +
  geom_errorbar(aes(ymin=Q2.5, ymax=Q97.5), position=position_dodge(), size=1, width=.5) +
  geom_point(shape=21, size=4, fill='violet') +
  #geom_hline(yintercept=50, linetype=2) +
  xlab("") +
  ylab('Probability of late prosaccade') +
  #ylim(0,100) +
  theme_bw () +
  theme(panel.grid = element_blank())
```

But what we are really interested in is COMPARING (=contrasts between ages 0 and 1)
Contrasts between age - we want to look at the posterior ON ITS CONTRAST
we use the same fitted function as before but we don't summarize it, so instead of summarizing the posterior we get the full posterior:

```{r}
fit1 = as.data.frame(fitted(late_pro_prob_ac_withoutprior_withouttrt, newdata = newdata, re_formula = NA, summary = FALSE))
colnames(fit1) = newdata$age
head(fit1)
#this is basically the MCMC chain but converted from regression coefficients for fitted values for each age. 

#If we want to compare old people with young people we can compare them for each step in MCMC chain and then we get the posterior on the contrast between them.
#We take for each step particular estimate and repeat this operation for each row.
old_vs_young = fit1[,"1"] - fit1[,"0"] 

#we can obtain a posterior distribution of this contrast and summarized it:
hist(old_vs_young)
plot(density(old_vs_young))
quantile(old_vs_young, probs = c(.5, .025, .975)) 

#the other way
young_vs_old = 1 - old_vs_young
hist(young_vs_old)
plot(density(young_vs_old))
quantile(young_vs_old, probs = c(.5, .025, .975)) 
```

"inhib_fail_prob"

models:
```{r}
#models with priors
prior1 <- brms:::set_prior("cauchy(0,2.5)", class="b")
prior2 <- brms:::set_prior("cauchy(0,2)", class="b")
prior3 <- brms:::set_prior("cauchy(0,1)", class="b")

#model without prior and without test_retest
inhib_fail_prob_ac_withoutprior_withouttrt<- brm(inhib_fail_prob  ~ 1 + age, data = antisaccades, family = Beta(),save_all_pars = TRUE)

#model with test_retest and with prior 
inhib_fail_prob_ac_withtestrt_withprior<- brm(inhib_fail_prob  ~ 1 + age +test_retest, data = antisaccades, family = Beta(),save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with prior and without test_retest
inhib_fail_prob_ac_withprior_withouttrt<- brm(inhib_fail_prob  ~ 1 + age, data = antisaccades, family = Beta(),save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with test_retest and without prior 
inhib_fail_prob_ac_withtestrt_withoutprior<- brm(inhib_fail_prob  ~ 1 + age +test_retest, data = antisaccades, family = Beta(),save_all_pars = TRUE)

```

summaries & plots of the models
```{r}
#model without prior and without test_retest
summary(inhib_fail_prob_ac_withoutprior_withouttrt)
plot(inhib_fail_prob_ac_withoutprior_withouttrt)

#model with test_retest and with prior 
summary(inhib_fail_prob_ac_withtestrt_withprior)
plot(inhib_fail_prob_ac_withtestrt_withprior)

#model with prior and without test_retest
summary(inhib_fail_prob_ac_withprior_withouttrt)
plot(inhib_fail_prob_ac_withprior_withouttrt)

#model with test_retest and without prior 
summary(inhib_fail_prob_ac_withtestrt_withoutprior)
plot(inhib_fail_prob_ac_withtestrt_withoutprior)

```

In further diagnostic I'll use model without test-retest and without prior
```{r}
fitted_values_inhib_fail_prob_ac_withoutprior_withouttrt <- fitted(inhib_fail_prob_ac_withoutprior_withouttrt)

#Y- probability that we want to model for each person
dat_fitted_values_inhib_fail_prob_ac_withoutprior_withouttrt <- as.data.frame(cbind(Y = standata(inhib_fail_prob_ac_withoutprior_withouttrt)$Y, fitted_values_inhib_fail_prob_ac_withoutprior_withouttrt))

ggplot(dat_fitted_values_inhib_fail_prob_ac_withoutprior_withouttrt) + geom_point(aes(x = Estimate, y = Y))

ppinhib_fail_prob_ac_withoutprior_withouttrt = brms::pp_check(inhib_fail_prob_ac_withoutprior_withouttrt,nsamples = 100)

marginaleffects_inhib_fail_prob_ac_withoutprior_withouttrt <- 
  brms::marginal_effects(inhib_fail_prob_ac_withoutprior_withouttrt, points = TRUE)
marginaleffects_inhib_fail_prob_ac_withoutprior_withouttrt

newdata_inhib_fail_prob_ac_withoutprior_withouttrt = data.frame(age = levels(antisaccades$age))

fit_inhib_fail_prob_ac_withoutprior_withouttrt = fitted(
 inhib_fail_prob_ac_withoutprior_withouttrt,
   newdata = newdata_inhib_fail_prob_ac_withoutprior_withouttrt,
   re_formula = NA,
 summary = TRUE)

df_plot2 = cbind(newdata_inhib_fail_prob_ac_withoutprior_withouttrt, fit_inhib_fail_prob_ac_withoutprior_withouttrt)

ggplot(df_plot2, aes(x = age, y = Estimate)) +
  geom_violin(data=antisaccades, aes(x=age, y=inhib_fail_prob), alpha=0.5, color="gray70", fill='gray95') +
  geom_jitter(data=antisaccades, aes(x=age, y=inhib_fail_prob), alpha=0.3, position = position_jitter(width = 0.07)) +
  geom_errorbar(aes(ymin=Q2.5, ymax=Q97.5), position=position_dodge(), size=1, width=.5) +
  geom_point(shape=21, size=4, fill='violet') +
  #geom_hline(yintercept=50, linetype=2) +
  xlab("") +
  ylab('Probability of inhib. fail') +
  #ylim(0,100) +
  theme_bw () +
  theme(panel.grid = element_blank())

```
Contrasts:
```{r}
fit2 = as.data.frame(fitted(inhib_fail_prob_ac_withoutprior_withouttrt, newdata = newdata_inhib_fail_prob_ac_withoutprior_withouttrt, re_formula = NA, summary = FALSE))
colnames(fit2) = newdata_inhib_fail_prob_ac_withoutprior_withouttrt$age
head(fit2)
#this is basically the MCMC chain but converted from regression coefficients for fitted values for each age. 

old_vs_young2 = fit2[,"1"] - fit2[,"0"] 

#we can obtain a posterior distribution of this contrast and summarized it:
hist(old_vs_young2)
plot(density(old_vs_young2))
quantile(old_vs_young2, probs = c(.5, .025, .975)) 

#the other way
young_vs_old2 = 1 - old_vs_young2
hist(young_vs_old2)
plot(density(young_vs_old2))
quantile(young_vs_old2, probs = c(.5, .025, .975)) 
```
Anti_rt
```{r}
#models with priors
prior1 <- brms:::set_prior("cauchy(0,2.5)", class="b")
prior2 <- brms:::set_prior("cauchy(0,2)", class="b")
prior3 <- brms:::set_prior("cauchy(0,1)", class="b")

#model without prior and without test_retest
anti_rt_ac_withoutprior_withouttrt<- brm(anti_rt  ~ 1 + age, data = antisaccades,save_all_pars = TRUE)

#model with test_retest and with prior 
anti_rt_ac_withtestrt_withprior<- brm(anti_rt  ~ 1 + age +test_retest, data = antisaccades,save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with prior and without test_retest
anti_rt_ac_withprior_withouttrt <- brm(anti_rt  ~ 1 + age, data = antisaccades,,save_all_pars = TRUE, sample_prior=T, prior=prior1)

#model with test_retest and without prior 
anti_rt_ac_withtestrt_withoutprior<- brm(anti_rt ~ 1 + age +test_retest, data = antisaccades,save_all_pars = TRUE)

```
In further diagnostic I'll use model without test-retest and without prior

```{r}
fitted_values_anti_rt_ac_withoutprior_withouttrt <- fitted(anti_rt_ac_withoutprior_withouttrt)

#Y- probability that we want to model for each person
dat_fitted_values_anti_rt_ac_withoutprior_withouttrt <- as.data.frame(cbind(Y = standata(anti_rt_ac_withoutprior_withouttrt)$Y, fitted_values_anti_rt_ac_withoutprior_withouttrt))
anti_rt_ac_withoutprior_withouttrt + geom_point(aes(x = Estimate, y = Y))

ppanti_rt_ac_withoutprior_withouttrt = brms::pp_check(anti_rt_ac_withoutprior_withouttrt,nsamples = 100)

marginaleffects_anti_rt_ac_withoutprior_withouttrt <- 
  brms::marginal_effects(anti_rt_ac_withoutprior_withouttrt, points = TRUE)
marginaleffects_anti_rt_ac_withoutprior_withouttrt

newdata_anti_rt_ac_withoutprior_withouttrt = data.frame(age = levels(antisaccades$age))

fit_anti_rt_ac_withoutprior_withouttrt = fitted(
 anti_rt_ac_withoutprior_withouttrt,
   newdata = newdata_anti_rt_ac_withoutprior_withouttrt,
   re_formula = NA,
 summary = TRUE)

df_plot3 = cbind(newdata_anti_rt_ac_withoutprior_withouttrt, fit_anti_rt_ac_withoutprior_withouttrt)

ggplot(df_plot3, aes(x = age, y = Estimate)) +
  geom_violin(data=antisaccades, aes(x=age, y=anti_rt), alpha=0.5, color="gray70", fill='gray95') +
  geom_jitter(data=antisaccades, aes(x=age, y=anti_rt), alpha=0.3, position = position_jitter(width = 0.07)) +
  geom_errorbar(aes(ymin=Q2.5, ymax=Q97.5), position=position_dodge(), size=1, width=.5) +
  geom_point(shape=21, size=4, fill='violet') +
  #geom_hline(yintercept=50, linetype=2) +
  xlab("") +
  ylab('anti rt') +
  #ylim(0,100) +
  theme_bw () +
  theme(panel.grid = element_blank())

```

Contrasts:
```{r}
fit3 = as.data.frame(fitted(anti_rt_ac_withoutprior_withouttrt, newdata = newdata_anti_rt_ac_withoutprior_withouttrt, re_formula = NA, summary = FALSE))
colnames(fit3) = newdata_anti_rt_ac_withoutprior_withouttrt$age
head(fit3)
#this is basically the MCMC chain but converted from regression coefficients for fitted values for each age. 

old_vs_young3 = fit3[,"1"] - fit3[,"0"] 

#we can obtain a posterior distribution of this contrast and summarized it:
hist(old_vs_young3)
plot(density(old_vs_young3))
quantile(old_vs_young2, probs = c(.5, .025, .975)) 

#the other way
young_vs_old3 = 1 - old_vs_young3
hist(young_vs_old3)
plot(density(young_vs_old3))
quantile(young_vs_old3, probs = c(.5, .025, .975)) 
```


```{r}
```

